HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_2.tex

	\textbf{Author response:} We understand this remark. As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test. It is then difficult to propose different splits (using rolling windows for instance) unless the forecast horizon is reduced. However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry.

In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set. A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.\\

	\item {\em ``It seems that there is no concept of trend birth and death in the proposed dataset. It would be nice if the authors can clarify if that is true and why is that the case
.''} \medskip

	\textbf{Author response:} We agree with the referee. Detecting trend birth and death is one of the main challenge of the fashion industry. Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue. To clarify this point, a new part in the appendix was added where 4 sub-samples of the Fashion dataset are built and forecasted separately. One of them is called \textit{disrupting} time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data. We define them as follows: using the \textit{snaive} model, a prediction of the last year and its linked MASE is computed for each trend. The \textit{dirsupting} time series are the 1000 time series where the \textit{snaive} prediction reachs the highest MASE. On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches. Table~\ref{tab:fashionsubsample} presents these results and will be added in the revised version of the paper.\\		
\end{itemize}

@@

\begin{table}
  \caption{Results summary on a sub-sample of Fashion time series named \textit{disrupting} time series.}\vspace{0.5cm} 
 \centering
 \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{\textit{disrupting} time series}\\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 1.455 & -\\ 
	 \textit{thetam} && 1.314 & -\\ 
	 \textit{ets} && 1.27 & -\\ 
	 \textit{arima} && 1.256 & -\\ 
	 \textit{tbats} && 1.229 & -\\ 
	 \textit{hermes-thetam} && 1.209 & 0.005\\ 
	 \textit{hermes-ets} && 1.202 & 0.007\\ 
	 \textit{stlm} && 1.198 & -\\ 
	 \textit{hermes-tbats} && 1.195 & 0.01\\ 
	 \textit{prophet} && 1.193 & -\\ 
	 \textit{deepar} && 1.18 & 0.03\\ 
	 \textit{lstm} && 1.15 & 0.01\\ 
	 \textit{hermes-thetam-ws} && 1.145 & 0.019\\ 
	 \textit{hermes-ets-ws} && 1.131 & 0.024\\ 
	 \textit{hermes-tbats-ws} && 1.092 & 0.007\\ 
	 \textit{lstm-ws} && 1.086 & 0.009\\  \vspace{0.5cm}\\
  \end{tabular}\hspace{1cm}
  }
 \label{tab:fashionsubsample}
\end{table}

\subsection*{Broader Impact Concerns:}
\begin{itemize}
	\item {\em `The work releases a new dataset in the public domain, which is derived from social media activity of a large number of user across multiple regions. It would be in order if the authors clarify whether due to the data collection or the release of the fashion dataset, there will be any implications for individuals' privacy whose data were utilized for this work.`''} \medskip

	\textbf{Author response:} We thank the referee for this remark and several information concerning this issue were added in Section 2. The whole design of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation. Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process. Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down. \\		
\end{itemize}

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_1_tmlr_format.tex

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\textcolor{orange}{j'ai coupé la réponse en trois pour pouvoir respecter la limite de 5000 mots. L'endroit ou je peux ecrire la réponse ne compile pas les tableaux en latex par contre, je les ai donc enlevé. Pareil pour les citations que j'ai écrit en dur.}
\bigskip

Response to review (first part).\vspace{0.2cm}

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published. In the meantime, you can find below responses to some of the remarks:

- We acknowledge that we did not discuss enough the choice of per-time-series models in the paper. This comment has led to additional justifications and discussions, in particular we discuss the use of state space models. We highlight that the main limitation for this choice is the computational time required to train the per-time-series models. In addition, in the experiment section, a third HERMES variation is added using Thetam as the per-times-series model.

- Concerning the choice of per-times-series model, the main limitation is the computational time required to train these models, as the dataset contains thousands of time series. For instance, training a HMM with the EM algorithm, or training ARIMA on thousands of time series would increase significantly the computational cost. Concerning TBATS, Exponential smoothing and Thetam, correctly fitting them with existing Python packages is possible in an reasonable time, from a few minutes for exponential smoothing models to a couple of hours for TBATS. We believe that our experiment section, in particular with the additional simulations, highlights the flexibility of the hybrid approach and the numerical results motivate the use of TBATS eventhough other models could be used. To clarify this point in the paper, several justifications and comments were added in the text.

- Your third remark has led to the addition of 2 new methods as benchmarks. First, the Prophet method introduced in Taylor $\&$ Letham (2017) is trained and evaluated on the fashion dataset using the Python package 'prophet'. We show that it leads to poor results in comparison to our model on the whole fashion dataset, and a comparable accuracy on the use case where only 100 time series are accessible. Secondly, the recent DeepAR method introduced in Salinas et al. (2020) is added  and trained with the Python package 'Gluonts' (Alexandrov et al., 2020). This method shows striking results on the fashion dataset and is a strong competitor of the proposed hybrid approach.

Citation:

Alexander Alexandrov, Konstantinos Benidis, Michael Bohlke-Schneider, Valentin Flunkert, Jan Gasthaus, Tim Januschowski, Danielle C. Maddix, Syama Rangapuram, David Salinas, Jasper Schulz, Lorenzo Stella, Ali Caner Türkmen, and Yuyang Wang. GluonTS: Probabilistic and Neural Time Series Modeling in Python. Journal of Machine Learning Research, 21(116):1–6, 2020. URL http://jmlr.org/papers/v21/
19-820.html.

David Salinas, Valentin Flunkert, Jan Gasthaus, and Tim Januschowski. DeepAR: Probabilistic forecasting with autoregressive recurrent networks. International Journal of Forecasting, 36(3):1181–1191, 2020.

Sean Taylor and Benjamin Letham. Forecasting at scale. The American Statistician, 72, 09 2017. doi:10.1080/00031305.2017.1380080.

Response to review (second part).\vspace{0.2cm}

- We thank the referee for the remark concerning the analysis of diffrent types of time series. This comment led to a new part in the appendix where 4 sub-samples of the Fashion dataset are built and forecasted separately.
Their are defined as follows:
	- disrupting time series: In retail and fashion industries, a strategic issue is to correctly anticipate new trends that will burst or collapse in the next weeks, months or years. To detect these sub sample of trends in the Fashion dataset, the following approach is proposed: Using the 'snaive' model, a prediction of the last year and its linked MASE is computed for each trend. Finally, the dirsupting time series are the 1000 time series with the highest MASE.
	-stable time series: By contrast, a group a stable trend a presented. To define them, the same methodology as the previous group is used. We define them as the time series where the snaive prediction reachs the lowest MASE. 
	-seasonal time series: Another relevant group of time series is sequences showing a strong seasonal patern. So as to detect them, we compute for each trend the seasonality strength metric introduced in Wang et al. (2006). The seasonal time series group is the 1000 fashion time series with highest seasonality strength.
	-noisy time series: Finally, several time series of the Fashion dataset represent niche trends only worn and posted on social media by a few people. The average volume for these sequences is low resulting in sporadic and noisy time series difficult to forecast. In order to detect them, we use the seasonality and trend strenght metrics presented in Wang et al. (2006). For each time series, the average of these two quantities is computed and we define the time series group as the 1000 sequences with the lowest averages.
We added the predictions of each model on these sub-samples and extended the analysis of the hybrid approach, the fashion dataset and the use of external signals. A table showing the results of each method on the 4 sub-samples will be added in appendix as well as a section describing more precisely how the 4 samples are built.

Citation:

Xiaozhe Wang, Kate Smith, and Rob Hyndman. Characteristic-based clustering for time series data. Data mining and knowledge Discovery, 13:335–364, 2006.

Response to review (third part).\vspace{0.2cm}

- The point concerning the impact of the proposed work on the society and environement is now developed in the discussion section. We discuss the impact of training deep architectures and the computational cost of the proposed approach. However, we highlight that the aim of this work is to show that it is possible to better forecast and anticipate consumers behaviours in the retail and fashion industry. With a better anticipation of consumer needs, companies could better adjust their production, reduce massive wastes due to their overstocks and finally offset the environmental cost of this work.

- We thank the referee for the remark pointing out privacy issues of using social media images. Several information concerning this issue were added in Section 2. The whole creation of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation. Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process. Concerning the time series, all the trends names have been anonymized and only macro information such as the geolocalisation, the type of cloth and the gender are revealed publicly. Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down.

- Concerning the potential risks or biases of using social media data, we totally agree with the referee. First of all, an important part of this work was to design a correct normalization process to remove the most visible biases brought by social media. Then, by proposing time series splitted by geo zone, we have tried to propose an accurate representation of the diversity of behaviours that exists in each region. We acknowledge that the proposed geozones may seem large. A future work could be to built trends at country level. Finally, by proposing a global model to forecast all the fashion trends, it is possible that rare patterns may not be correctly learned by the proposed framework. A future relevant work would be to learn models with latent states and an unsupervised learning

### 2023-06-08 tmlr_submission/hermes_paper_revision/answers_reviewer_2_tmlr_format.tex

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

Response to review.\vspace{0.2cm}

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly when all reviews will be published. In the meantime, you can find below responses to some of the remarks:

- In fact, only results for methods without weak signals were presented on the smaller datasets in Table 4. The original idea was to illustrate that the proposed hybrid framework seems to be a better solution on small datasets than methods only using neural networks. However, we agree with the referee and for completeness, all the models and metrics presented on the whole Fashion dataset are now also presented in Table 4.

- We understand the remark concerning absence of results for multiple temporal splits of data. As the Fashion time series only have 5 years of historical data, Figure 6 illustrates that we have just enough historical data for the proposed split train/eval/test. It is then difficult to propose different splits (using rolling windows for instance) unless the forecast horizon is reduced. However, this option is not really relevant as clothes collection are usually prepared one year or more in advance in the fashion industry.  In order to evaluate the HERMES model on a different forecasting task, we propose the second application on the M4 dataset where the horizon is set to 13, the eval set is reduced and a moving window is applied on the training part of the time series to increase the size of the trainng set. A paragraph was added in the experiment section to clarify this point and highlight the difference between the Fashion application case and the M4's one.

- Detecting trend birth and death is one of the main challenge of the fashion industry. Thus, an aim of this work is to illustrate that analysing social media and influencers seems to be a promising way to tackle this issue. To clarify this point, a new part in the appendix was added where 4 sub-samples of the Fashion dataset are built and forecasted separately. One of them is called 'disrupting' time series and gathers the most difficult sequences to forecast: the fashion trends that burst or collapse on the last year of data. We define them as follows: using the 'snaive' model, a prediction of the last year and its linked MASE is computed for each trend. The  'dirsupting' time series are the 1000 time series where the 'snaive' prediction reachs the highest MASE. On this particular group, we show that methods using the influencers external signal reach the highest accuracy and largely outperforms the other approaches.

- We thank the referee for the remark on potential privacy issues resulting from the use of social media images. Several information concerning these issues were added in Section 2. The whole design of the dataset respects the privacy and data protection regulations, including the General Data Protection Regulation. Concerning the image recovery on social media, only public accounts have been analysed and no potential private information were used, saved or revealed during the whole process. Concerning the time series, as they represent aggregate and normalized signals, no users' personal information can be tracked down.

### 2023-06-28 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly. In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.

@@

\section*{Detailed responses}

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``The reliability of the data is important for the use of this data by third parties. Please explain in detail how the human processing was done. Also, to what extent can machine failures be included in image processing? Do humans correct them?''} \medskip

	\textbf{Author response:} \\

	\item {\em ``In publishing the data, it would be good to add a little more analysis of the characteristics of the data. For example, basic statistics for each market, statistics for the Weak signal $w^{f,i}_t$, etc.''} \medskip

	\textbf{Author response:} \\

	\item {\em ``It is written that represents the index of fashion trends, but it is unclear what exactly it refers to. Does it correspond to a product/item?''} \medskip

	\textbf{Author response:}\\

	\item {\em ``I didn't know what statistic was $\hat{y}^{c,g,m}$. Could you please explain it in detail?''} \medskip

	\textbf{Author response:}\\

	\item {\em ``It may be a good idea to modify the structure of Section 3. It is better to explain the hybrid model (4) at first.  Then, elaborate on the motivation behind the formulation of (4). The output of the RNN appears to represent the weights in summing $f^(.)$ and $\bar{y}^n_{T}$. Is that correct? Also, when is one of $y^{pred}$ and $y^{corr}$ more dominant than the other? The cost function described in Section 4.1 should be moved to Section 3.''} \medskip

	\textbf{Author response:}\\

	\item {\em ``It would be good to add a discussion of the limitations of this study. Other external factors could be various, such as advertisements. This study focuses on the correlation between weak signals and trends, not causality. This should be clearly stated. As seen in Figure 2, the effect of the external factor is accompanied by a time delay. It would be interesting to analyze how such time delays vary by fashion category and market. It would also be interesting to incorporate this into machine learning models.''} \medskip

	\textbf{Author response:}\\

	\item {\em ``In Table 2, it would be good to clarify which methods can handle weak signals and which cannot. Then, please clarify by experiment that it is effective to construct a hybrid model by the weighted sum of two terms as in the proposed method (4).''} \medskip

	\textbf{Author response:}\\

	\item {\em ``Minor issues: i)The term "causal inference" appears in the abstract, but it is not discussed in this study and should be changed to another term. ii) The proposed method, HERMES, does not specify what it stands for. iii) Please cite Figure 1 in the text. iv) Please change the "t" in "At each time t" in section 2.1 to italic.''} \medskip

	\textbf{Author response:} \textcolor{orange}{correction faites sauf pour la remarque sur HERMES. Peut etre que dans la réponse on pourra dire que c'est pour Hybird ERro-corrector Model with inclusion of External Signals ...}\\	
\end{itemize}
\end{document}

### 2023-06-28 tmlr_submission/hermes_paper_revision/hermes_paper.tex
add minor remarks of reviewer 3

\begin{abstract}
Developing models and algorithms to draw causal inference for time series is a long standing statistical problem. It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes. By tracking thousands of fashion trends on social media with state-of-the-art computer vision approaches, we propose a new model for fashion time series forecasting. Our contribution is  twofold. We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series. As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers. Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnotemark. Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals. This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \citep{makridakis2018}, and illustrates the benefit of the contribution of external weak signals.
\end{abstract}

@@

@@

Social media have appeared as an impressive data source to follow the evolution of fashion over the time. Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world. To do it automatically for thousands of trends, the following methodology was introduced. In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo. We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China. \textcolor{orange}{With compliance of the privacy and data protection, only public accounts are used and no potential private information are used, saved or revealed during the whole process.}
The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc. To do so, the following framework is designed.
\begin{enumerate}
    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture. This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}. Starting from weights trained on MS-COCO \citep{lin2014}, the model is fine-tuned with our data with a standard setup following the original paper.
    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details. We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc. These models are all based on the Xception architecture introduced in \citet{chollet2017}. So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task. Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
\end{enumerate}

@@

The 150 million of social media pictures are analyzed with this visual recognition pipeline. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$. As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

@@

\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with a several other approaches. the HERMES framework is evaluated on two different use cases.
\begin{itemize}
	\item A first application is proposed on the Fashion dataset. The HERMES model is trained at forecasting the fashion time series one year ahead (h=52). This use case is mostly guided by the fashion and retail industry where clothes collections are usually prepared one year or more in advance. As additional signals representing influencers behaviours are available, this allows  to set the focus on the ability of our framework to leverage these weak signals.
	\item A second application is proposed on the weekly dataset of the M4 competition \citep{makridakis2018}. Based on the competition's rules, the forecasting horizon is set to 13 and no external signals are available. Futhermore, the proposed times series come from different sectors and have variable lengths.
\end{itemize}
}

>>>>

\begin{abstract}
Developing models and algorithms to draw \textcolor{gray}{causal inference} \textcolor{orange}{predictions} for time series is a long standing statistical problem. It is crucial for many applications, in particular for fashion or retail industries, to make optimal inventory decisions and avoid massive wastes. By tracking thousands of fashion trends on social media with state-of-the-art computer vision approaches, we propose a new model for fashion time series forecasting. Our contribution is  twofold. We first provide publicly\footnote[1]{\url{https://anonymous.4open.science/r/HERMES-703F/}} an appealing \textcolor{gray}{fashion} dataset gathering \numberts\ weekly fashion time series. As influence dynamics are the key of emerging trend detection, we associate with each time series an external weak signal representing behaviours of influencers. Secondly, to leverage such a complex and rich dataset, we propose a new hybrid forecasting model\footnotemark. Our approach combines per-time-series parametric models with seasonal components and a global recurrent neural network to include sporadic external signals. This hybrid model provides state-of-the-art results on the proposed fashion dataset, on the weekly time series of the M4 competition \citep{makridakis2018}, and illustrates the benefit of the contribution of external weak signals.
\end{abstract}

@@

\textcolor{orange}{Social Networks have appeared as an impressive data source to follow the evolution of fashion over the time. Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world. To do it automatically for thousands of trends, the following methodology is introduced in this section and summarized in Figure~\ref{fig:pipeline}.}

@@

\textcolor{gray}{Social media have appeared as an impressive data source to follow the evolution of fashion over the time. Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world. To do it automatically for thousands of trends, the following methodology was introduced.} In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo. We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China. \textcolor{orange}{With compliance of the privacy and data protection, only public accounts are selected and no potential private information are used, saved or revealed during the whole process.}
The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc. To do so, the following framework is designed.
\begin{enumerate}
    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture. This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}. Starting from weights trained on MS-COCO \citep{lin2014}, the model is fine-tuned with our data with a standard setup following the original paper.
    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details. We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc. These models are all based on the Xception architecture introduced in \citet{chollet2017}. So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task. Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
\end{enumerate}

@@

The 150 million of social media pictures are analyzed with this visual recognition pipeline. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time $t$, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$. As an illustration, example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

@@

\textcolor{orange}{In this section, performance of the hybrid model are presented and compared with several other approaches. the HERMES framework is evaluated on two different use cases.
\begin{itemize}
	\item A first application is proposed on the Fashion dataset. The HERMES model is trained at forecasting the fashion time series one year ahead (h=52). This use case is mostly guided by the fashion and retail industry where clothes collections are usually prepared one year or more in advance. As additional signals representing influencers behaviours are available, this allows  to set the focus on the ability of our framework to leverage these weak signals.
	\item A second application is proposed on the weekly dataset of the M4 competition \citep{makridakis2018}. Based on the competition's rules, the forecasting horizon is set to 13 and no external signals are available. Futhermore, the proposed times series come from different sectors and have variable lengths.
\end{itemize}
}
